Type Error Telemetry at Scale

### 2023-09-24 programming23/paper.tex
move file count to footnote

\subsection{Telemetry records}
\label{s:telemetry-records}

@@

\begin{figure}[t]
  % ;; (list* (max* vv) (median < vv) mm (stddev/mean mm vv) (percentile* vv)))
  % ;; percentile* = 0.95 -- 0.99
  % #hash((editrange . (1156036 926 3007043/817 30975.40553032358 (0.95 8220) (0.96 9858) (0.97 13656) (0.98 18956) (0.99 34725)))
  %       (event-count . (6079 138 38689/135 582.5752201972966 (0.95 960) (0.96 1174) (0.97 1304) (0.98 1836) (0.99 3302)))
  %       (files . (54884 7678 55257996/4639 11853.650098459446 (0.95 40029) (0.96 42771) (0.97 45417) (0.98 48688) (0.99 51761)))
  %       (lines . (1089963 3115 38928947/5992 22364.75846303099 (0.95 18561) (0.96 25892) (0.97 27014) (0.98 29725) (0.99 50547)))
  %       (timespan . (1387897376 845648 591343604248/185705 15724745.722577972 (0.95 10696064) (0.96 12715468) (0.97 15596940) (0.98 21153924) (0.99 35450460))))
  %% NOTE: 3 records have +1M lines, all from one nocheck session, all with 3 files
  %% - session "30,762,216,447,324"
  %% NOTE: 133 records have +52K files, all from one nocheck session
  %% - session "330,172,870,224,081" 
  %% (2nd biggest has 41K files "31,650,473,913,529")

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l@{}r@{~}l}
                 & Files  &              &     Lines &             &    Edit Range & \\
    Mean [std]   & 11,911 & \stddev{12}  &     6,497 & \stddev{22} &         3,680 & \stddev{31} \\
    Median       &  7,678 &              &     3,115 &             &           926 & \\
    \pct{99}     & 51,761 &              &    50,547 &             &        34,725 & \\
    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

\Cref{f:codebase-size} summarizes the size of projects in the dataset.
The top half of the figure reports the mean, standard deviation, median,
and \percentile{99} for the number of files,\todo{There are
  1000s of files?!? More files than lines? Makes no sense.} lines, and lines in edit range.
The bottom half shows zoomed-in distributions of the file, line, and edit range
numbers.
For example, the x-axis of the first plot ranges from 0 to 1,000 files and
the y-axis counts up to 1,000 telemetry records.

There is a huge amount of variation across projects.
The largest ones have over 50,000 files, and
there are many small ones with 1 file and/or 1 line of code.
Unsurprisingly, the numbers come with large standard
deviations.\todo{Which is not shown!}
The median values are more reasonable, with roughly 3,000 lines of code
and 1,000 lines in edit ranges, but still have a large number of files: over 7,000.
One source of variation is that some developers use Luau scripts as a way
to store data, writing a module that exports one huge array, typically
defined on a single line. Such data storage scripts provide a challenge for
script tooling.\todo{No idea what's said here.}

%% The high number of files may be because creators define many components to
%% build a Roblox experience and put these components in separate files.
%% (\FILL{} still that's a lot of components ... any better guesses?)

%% (\FILL{} doublecheck file sizes)
% That seems way off, not sure we're seeing so many files :/

@@

@@

\subsection{Forced Strict Errors}

\FILL{} I (ben) think we need to talk more about forced strict errors here, or soon.
Otherwise people will forget they exist in the data.

>>>>

\subsection{Telemetry Records}
\label{s:telemetry-records}

\begin{figure}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|}\midrule
    meta & size & te count & fs count & te 0 & te 1 & te 2 \ldots
    \\\midrule
  \end{tabular}
  \caption{Struture of a telemetry record}
  \label{f:tdata}
\end{figure}

@@

\begin{figure}[t]\centering
  % ;; (list* (max* vv) (median < vv) mm (stddev/mean mm vv) (percentile* vv)))
  % ;; percentile* = 0.95 -- 0.99
  % #hash((editrange . (1156036 926 3007043/817 30975.40553032358 (0.95 8220) (0.96 9858) (0.97 13656) (0.98 18956) (0.99 34725)))
  %       (event-count . (6079 138 38689/135 582.5752201972966 (0.95 960) (0.96 1174) (0.97 1304) (0.98 1836) (0.99 3302)))
  %       (files . (54884 7678 55257996/4639 11853.650098459446 (0.95 40029) (0.96 42771) (0.97 45417) (0.98 48688) (0.99 51761)))
  %       (lines . (1089963 3115 38928947/5992 22364.75846303099 (0.95 18561) (0.96 25892) (0.97 27014) (0.98 29725) (0.99 50547)))
  %       (timespan . (1387897376 845648 591343604248/185705 15724745.722577972 (0.95 10696064) (0.96 12715468) (0.97 15596940) (0.98 21153924) (0.99 35450460))))
  %% NOTE: 3 records have +1M lines, all from one nocheck session, all with 3 files
  %% - session "30,762,216,447,324"
  %% NOTE: 133 records have +52K files, all from one nocheck session
  %% - session "330,172,870,224,081" 
  %% (2nd biggest has 41K files "31,650,473,913,529")

%% Files has HUGE numbers thanks to data assets. Forget it.
% Files  &              &
% 11,911 & \stddev{12}  &
%  7,678 &              &
% 51,761 &              &
%   & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l}
                 &  Lines &             &    Edit Range & \\
    Mean [std]   &  6,497 & \stddev{22} &         3,680 & \stddev{31} \\
    Median       &  3,115 &             &           926 & \\
    \pct{99}     & 50,547 &             &        34,725 & \\
    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
      & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

\Cref{f:codebase-size} summarizes the size of projects in the dataset.
The top half of the figure reports the mean, standard deviation, median,
and \percentile{99} for the number of lines
and lines in edit range.\footnote{The data also contains the number of files in
each project, but these numbers are difficult to relate to typechecking because
projects may contain hundreds of files that define data assets.  For the
record, the median file count is 7,678 and the 99th percentile is 51,761 files.
}
The bottom half shows zoomed-in distributions of the line and edit range
sizes.
For example, the x-axis of the first plot ranges from 0 to 1,000 lines and
the y-axis counts up to 1,000 telemetry records.

There is a huge amount of variation across projects.
The largest ones have over 50,000 lines of code
while the smallest have merely 1 line of code.
Unsurprisingly, the numbers come with large standard
deviations~([std] in~\cref{f:codebase-size}).
The median values are more reasonable, with roughly 3,000 lines of code
and 1,000 lines in edit ranges.

@@

\subsection{Forced Strict Errors by Mode}

FILL

How do the 72 million forced strict divide across modes?

What about type errors, same distribution?!

@@
